A Non-local Bayesian Video Denoising Method

### 2015-08-19 doc/201507_tip/paper.tex
[doc] Updated grayscale PSNR tables with result of second attempt.
- Figures for first stage parameter selection (first attemp) based on derf average instead of bus.
- References added.

\begin{figure*}[htpb!]
	\begin{center}
		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s10_bus.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s20_bus.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s40_bus.eps}\\
		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s10_bus.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s20_bus.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s40_bus.eps}\\
	\end{center}
	\caption{Same as Figure \ref{fig:rank-nsim-image-stage2} but for the first stage.}
	\label{fig:rank-nsim-image-stage1}
\end{figure*}

@@

			                      & LZD                  & \bsic{     } &       36.45  & \bsic{     } &       40.49   & \bsic{     } &       34.46   & \bsic{     } &       37.03  &              &               &              &              & \bsic{     } &       37.13  \\

@@

			                      & V-BM4D-mp            & \bsic{34.32} &       34.95  & \bsic{36.77} &       37.48   & \bsic{32.20} &       32.01   & \bsic{33.99} &       34.11  & \bsic{37.58} &       37.85   & \bsic{33.47} &       33.68  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 2$     & \bsic{34.33} &       34.62  & \Bsic{todo } &       todo    & \Bsic{todo } &       todo    & \bsic{34.44} &       34.67  & \Bsic{todo } &       todo    & \Bsic{33.82} & \Best{34.23} & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 3$     & \Bsic{34.53} &       35.15  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{34.74} &       35.31  & \bsic{todo } & \Best{todo }  & \Bsic{33.81} & \Best{34.29} & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \bsic{34.18} & \Best{35.32} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{34.41} & \Best{35.54} & \bsic{todo } &       todo    & \bsic{33.47} &       34.13  & \bsic{todo } &       todo   \\\hline

@@

			                      & LZD                  & \bsic{     } &       33.36  & \bsic{     } &       37.52   & \bsic{     } &       31.35   & \bsic{     } &       33.47  &              &               &              &              & \bsic{     } &       34.08  \\

@@

			                      & V-BM4D-mp            & \bsic{30.54} &       31.08  & \bsic{32.18} &       33.46   & \bsic{28.12} &       28.32   & \bsic{29.67} &       30.49  & \bsic{33.62} &       34.54   & \bsic{29.04} &       29.69  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 2$     & \Bsic{30.73} &       31.24  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{29.83} &       30.34  & \Bsic{todo } & \Best{todo }  & \Bsic{29.38} &       29.90  & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 3$     & \Bsic{30.82} &       31.66  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{30.15} &       31.09  & \bsic{todo } & \Best{todo }  & \Bsic{29.33} & \Best{30.02} & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \bsic{30.25} & \Best{31.69} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{29.74} & \Best{31.35} & \bsic{todo } &       todo    & \bsic{28.89} & \Best{29.97} & \bsic{todo } &       todo   \\\hline

@@

			                      & LZD                  & \bsic{     } &       31.62  & \bsic{     } &       36.05   & \bsic{     } &       29.09   & \bsic{     } &       30.36  &              &               &              &              & \bsic{     } &       32.25  \\

@@

			                      & V-BM4D-mp            & \bsic{28.89} &       29.37  & \bsic{29.56} &       31.02   & \bsic{25.63} &       26.20   & \bsic{26.73} &       27.99  & \bsic{30.99} &       32.30   & \bsic{26.39} &       27.34  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 2$     & \Bsic{todo } &       todo   & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{todo } &       todo   & \Bsic{todo } & \Best{todo }  & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 3$     & \Bsic{todo } &       todo   & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{todo } &       todo   & \bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo } & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \bsic{todo } & \Best{todo } & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{todo } & \Best{todo } & \bsic{todo } &       todo    & \bsic{todo } & \Best{todo } & \bsic{todo } &       todo   \\\hline

@@

			                      & LZD                  & \bsic{     } &       30.79  & \bsic{     } &       35.12   & \bsic{     } &       27.56   & \bsic{     } &       28.93  &              &               &              &              & \bsic{     } &       31.16  \\

@@

			                      & V-BM4D-mp            & \bsic{27.67} &       28.38  & \bsic{27.81} &       29.37   & \bsic{23.68} &       24.59   & \bsic{24.64} &       26.02  & \bsic{29.02} &       30.58   & \bsic{24.47} &       25.64  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 2$     & \bsic{27.14} &       28.15  & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{25.43} &       26.06  & \bsic{todo } &       todo    & \bsic{25.18} &       25.81  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 3$     & \bsic{27.63} &       28.62  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{26.15} &       26.94  & \Bsic{todo } & \Best{todo }  & \Bsic{25.44} & \Best{26.12} & \Bsic{todo } & \Best{todo } \\
			                      & VNLB   $s_t = 4$     & \Bsic{27.81} & \Best{28.86} & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \Bsic{26.45} & \Best{27.46} & \Bsic{todo } & \Best{todo }  & \Bsic{25.50} & \Best{26.24} & \Bsic{todo } & \Best{todo } \\\hline

@@

In this section we present results obtained with the proposed
method on some classic test sequences with Gaussian noise added.

@@

We compared our method with CIFIC \cite{Dai2013} and V-BM4D \cite{Maggioni2012}, two recent
state-of-the-art methods. For V-BM4D, we show results corresponding to two
different choices of parameters. The method labeled V-BM4D-\cite{Maggioni2012}
corresponds to the results reported
in \cite{Maggioni2012}. The result labeled V-BM4D-mp was
obtained using the implementation available online \cite{bm4dcode}. This
implementation provides three parameter profiles of increasing quality and
complexity: ``low complexity profile'', ``normal profile'' and ``modified
profile''. We show the results obtained with the modified (V-BM4D-mp) profile.

@@

\begin{table*}[htp!]
	\begin{center}
		{%\small
		\renewcommand{\tabcolsep}{1.6mm}
		\renewcommand{\arraystretch}{1.3}
		\begin{tabular}{ c | l |c c | c c | c c | c c | c c}
			\hline
			\rule{0pt}{10pt}         & Sequence          &\multicolumn{2}{c|}{Bamboo 1}&\multicolumn{2}{c|}{Bandage 1}&\multicolumn{2}{c|}{Cave 4} &\multicolumn{2}{c|}{Market 5}& \multicolumn{2}{c}{Average} \\
			\rule{0pt}{10pt}$\sigma$ & Method            & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         \\\hline
			\multirow{1}{*}{$10$}
			                      & V-BM4D-mp            & \bsic{37.47} &       38.85  & \bsic{38.67} &       40.02  & \bsic{37.30} &       38.40  & \bsic{39.52} &       40.41  & \bsic{38.24} &       39.42  \\
			                      & VNLB   $s_t = 1$     & \bsic{37.48} &       39.74  & \bsic{39.85} &       41.83  & \Bsic{38.80} & \Best{40.82} & \Bsic{42.16} & \Best{44.10} & \bsic{39.57} &       41.62  \\
			                      & VNLB   $s_t = 2$     & \bsic{39.01} &       41.10  & \Bsic{40.74} & \Best{42.40} & \bsic{38.70} &       40.65  & \Bsic{42.23} & \Best{44.14} & \Bsic{40.17} & \Best{42.07} \\
			                      & VNLB   $s_t = 3$     & \bsic{39.40} & \Best{41.37} & \Bsic{40.74} & \Best{42.36} & \bsic{38.50} &       40.35  & \Bsic{42.17} & \Best{44.08} & \Bsic{40.20} & \Best{42.04} \\
			                      & VNLB   $s_t = 4$     & \Bsic{39.44} & \Best{41.33} & \bsic{40.51} &       42.12  & \bsic{38.30} &       40.05  & \bsic{42.07} &       43.97  & \bsic{40.08} &       41.86  \\\hline
%
			\multirow{1}{*}{$20$}
			                      & V-BM4D-mp            & \bsic{33.23} &       34.70  & \bsic{34.63} &       35.98  & \bsic{33.85} &       34.94  & \bsic{35.30} &       36.13  & \bsic{34.25} &       35.44  \\
			                      & VNLB   $s_t = 1$     & \bsic{33.19} &       35.53  & \bsic{35.60} &       37.76  & \bsic{35.35} &       37.31  & \bsic{37.90} &       39.88  & \bsic{35.51} &       37.62  \\
			                      & VNLB   $s_t = 2$     & \bsic{34.95} &       36.93  & \bsic{37.03} &       38.69  & \Bsic{35.60} & \Best{37.52} & \Bsic{38.60} & \Best{40.52} & \bsic{36.55} &       38.41  \\
			                      & VNLB   $s_t = 3$     & \bsic{35.48} &       37.40  & \Bsic{37.27} & \Best{38.86} & \Bsic{35.54} & \Best{37.43} & \Bsic{38.60} & \Best{40.54} & \Bsic{36.72} & \Best{38.56} \\
			                      & VNLB   $s_t = 4$     & \Bsic{35.65} & \Best{37.54} & \Bsic{37.26} & \Best{38.84} & \bsic{35.44} &       37.32  & \Bsic{38.50} & \Best{40.48} & \Bsic{36.71} & \Best{38.55} \\\hline
%
			\multirow{1}{*}{$40$}
			                      & V-BM4D-mp            & \bsic{29.07} &       30.46  & \bsic{30.45} &       31.82  & \bsic{30.50} &       31.57  & \bsic{30.93} &       31.74  & \bsic{30.24} &       31.40  \\
			                      & VNLB   $s_t = 1$     & \bsic{29.25} &       31.57  & \bsic{31.44} &       33.67  & \bsic{31.70} &       33.70  & \bsic{33.47} &       35.44  & \bsic{31.46} &       33.60  \\
			                      & VNLB   $s_t = 2$     & \bsic{31.18} &       32.99  & \bsic{33.40} &       35.06  & \Bsic{32.60} & \Best{34.61} & \bsic{34.76} &       36.63  & \bsic{32.98} &       34.82  \\
			                      & VNLB   $s_t = 3$     & \bsic{31.69} &       33.46  & \Bsic{33.76} & \Best{35.32} & \Bsic{32.70} & \Best{34.69} & \Bsic{34.91} & \Best{36.79} & \Bsic{33.27} & \Best{35.07} \\
			                      & VNLB   $s_t = 4$     & \Bsic{31.88} & \Best{33.64} & \Bsic{33.82} & \Best{35.37} & \Bsic{32.70} & \Best{34.66} & \Bsic{34.89} & \Best{36.77} & \Bsic{33.22} & \Best{35.11} \\\hline
		\end{tabular}}
	\end{center}
	\caption{PSNRs and TCEs obtained for the four CGI sequences from MPI
	Sintel's database. See text for details.}
	\label{tab:sintel}
\end{table*}

>>>>

\begin{figure*}[htpb!]
	\begin{center}
		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s10_average_derf.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s20_average_derf.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s40_average_derf.eps}\\
		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s10_average_derf.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s20_average_derf.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s40_average_derf.eps}\\
	\end{center}
	\caption{Same as Figure \ref{fig:rank-nsim-image-stage2} but for the first stage.}
	\label{fig:rank-nsim-image-stage1}
\end{figure*}

@@

			                      & LZD                  & \bsic{     } & \Best{36.45} & \bsic{     } & \Best{40.49}  & \bsic{     } & \Best{34.46}  & \bsic{     } & \Best{37.03} &              &               &              &              & \bsic{     } &       37.13  \\

@@

			                      & V-BM4D-mp            & \Bsic{34.32} &       34.95  & \Bsic{36.77} &       37.48   & \bsic{32.20} &       32.01   & \bsic{33.99} &       34.11  & \Bsic{37.58} &       37.85   & \bsic{33.47} &       33.68  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{32.99} &       33.29  & \bsic{34.62} &       35.15   & \bsic{30.80} &       31.22   & \bsic{32.34} &       32.79  & \bsic{36.21} &       37.72   & \bsic{33.20} &       33.79  & \bsic{todo } &       todo   \\
										 & VNLB   $s_t = 2$     & \Bsic{34.35} &       34.68  & \bsic{35.87} &       36.62   & \bsic{32.41} &       32.92   & \Bsic{34.26} &       34.78  & \bsic{36.86} & \Best{38.55}  & \Bsic{33.73} & \Best{34.38} & \Bsic{todo } &       todo   \\
										 & VNLB   $s_t = 3$     & \Bsic{34.34} &       35.23  & \bsic{35.63} &       37.08   & \bsic{32.39} &       33.18   & \bsic{34.02} &       35.25  & \bsic{36.57} & \Best{38.45}  & \bsic{33.45} & \Best{34.36} & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \Bsic{34.25} &       35.40  & \bsic{35.39} &       37.21   & \Bsic{32.54} &       33.10   & \bsic{34.03} &       35.48  & \bsic{36.05} &       38.27   & \bsic{33.39} &       34.10  & \bsic{todo } &       todo   \\\hline
%			                      & VNLB   $s_t = 2$     & \bsic{34.33} &       34.62  & \Bsic{todo } &       todo    & \Bsic{todo } &       todo    & \bsic{34.44} &       34.67  & \Bsic{todo } &       todo    & \Bsic{33.82} & \Best{34.23} & \Bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 3$     & \Bsic{34.53} &       35.15  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{34.74} &       35.31  & \bsic{todo } & \Best{todo }  & \Bsic{33.81} & \Best{34.29} & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 4$     & \bsic{34.18} & \Best{35.32} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{34.41} & \Best{35.54} & \bsic{todo } &       todo    & \bsic{33.47} &       34.13  & \bsic{todo } &       todo   \\\hline

@@

			                      & LZD                  & \bsic{     } & \Best{33.36} & \bsic{     } & \Best{37.52}  & \bsic{     } & \Best{31.35}  & \bsic{     } & \Best{33.47} &              &               &              &              & \bsic{     } &       34.08  \\

@@

			                      & V-BM4D-mp            & \bsic{30.54} &       31.08  & \Bsic{32.18} &       33.46   & \Bsic{28.12} &       28.32   & \Bsic{29.67} &       30.49  & \Bsic{33.62} &       34.54   & \bsic{29.04} &       29.69  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{29.62} &       30.16  & \bsic{30.76} &       31.54   & \bsic{26.17} &       26.56   & \bsic{27.89} &       28.39  & \bsic{32.41} &       33.77   & \bsic{28.69} &       29.26  & \bsic{todo } &       todo   \\
										 & VNLB   $s_t = 2$     & \Bsic{30.81} &       31.37  & \bsic{31.98} &       33.08   & \bsic{27.89} &       28.41   & \Bsic{29.69} &       30.41  & \bsic{33.17} & \Best{34.97}  & \Bsic{29.32} & \Best{30.00} & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 3$     & \bsic{29.88} &       31.62  & \bsic{30.60} &       33.05   & \bsic{27.50} &       28.89   & \bsic{29.02} &       30.86  & \bsic{31.23} &       34.26   & \bsic{28.51} & \Best{30.08} & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \bsic{29.49} &       31.64  & \bsic{30.10} &       32.94   & \bsic{27.47} &       29.07   & \bsic{28.86} &       31.12  & \bsic{30.51} &       33.88   & \bsic{28.26} & \Best{30.03} & \bsic{todo } &       todo   \\\hline
%			                      & VNLB   $s_t = 2$     & \Bsic{30.73} &       31.24  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{29.83} &       30.34  & \Bsic{todo } & \Best{todo }  & \Bsic{29.38} &       29.90  & \Bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 3$     & \Bsic{30.82} &       31.66  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{30.15} &       31.09  & \bsic{todo } & \Best{todo }  & \Bsic{29.33} & \Best{30.02} & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 4$     & \bsic{30.25} & \Best{31.69} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{29.74} & \Best{31.35} & \bsic{todo } &       todo    & \bsic{28.89} & \Best{29.97} & \bsic{todo } &       todo   \\\hline

@@

			                      & LZD                  & \bsic{     } & \Best{31.62} & \bsic{     } & \Best{36.05}  & \bsic{     } & \Best{29.09}  & \bsic{     } & \Best{30.36} &              &               &              &              & \bsic{     } &       32.25  \\

@@

			                      & V-BM4D-mp            & \Bsic{28.89} &       29.37  & \Bsic{29.56} &       31.02   & \Bsic{25.63} &       26.20   & \bsic{26.73} &       27.99  & \Bsic{30.99} &       32.30   & \bsic{26.39} &       27.34  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{27.32} &       28.20  & \bsic{27.94} &       29.14   & \bsic{23.62} &       23.96   & \bsic{25.42} &       25.82  & \bsic{29.50} &       31.08   & \bsic{26.14} &       26.69  & \bsic{todo } &       todo   \\
										 & VNLB   $s_t = 2$     & \bsic{28.65} &       29.51  & \Bsic{29.55} &       30.93   & \bsic{25.33} &       25.78   & \Bsic{27.31} &       27.90  & \bsic{30.70} & \Best{32.63}  & \Bsic{26.99} &       27.55  & \Bsic{todo } &       todo   \\
										 & VNLB   $s_t = 3$     & \bsic{27.49} &       29.71  & \bsic{27.91} &       30.91   & \bsic{24.75} &       26.36   & \bsic{26.30} &       28.43  & \bsic{28.45} &       31.95   & \bsic{25.95} & \Best{27.72} & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \bsic{26.92} &       29.64  & \bsic{27.28} &       30.73   & \bsic{24.60} &       26.60   & \bsic{26.04} &       28.68  & \bsic{27.61} &       31.50   & \bsic{25.57} & \Best{27.71} & \bsic{todo } &       todo   \\\hline

@@

			                      & LZD                  & \bsic{     } & \Best{30.79} & \bsic{     } & \Best{35.12}  & \bsic{     } & \Best{27.56}  & \bsic{     } & \Best{28.93} &              &               &              &              & \bsic{     } &       31.16  \\

@@

			                      & V-BM4D-mp            & \Bsic{27.67} &       28.38  & \Bsic{27.81} &       29.37   & \Bsic{23.68} &       24.59   & \bsic{24.64} &       26.02  & \Bsic{29.02} &       30.58   & \bsic{24.47} &       25.64  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{25.65} &       26.83  & \bsic{25.97} &       27.49   & \bsic{21.89} &       22.25   & \bsic{23.57} &       24.11  & \bsic{27.32} &       29.03   & \bsic{24.27} &       24.97  & \bsic{todo } &       todo   \\
										 & VNLB   $s_t = 2$     & \bsic{27.09} &       28.27  & \bsic{27.67} &       29.46   & \bsic{23.56} &       24.06   & \Bsic{25.48} &       26.17  & \bsic{28.64} & \Best{30.90}  & \Bsic{25.21} &       25.89  & \bsic{todo } &       todo   \\
										 & VNLB   $s_t = 3$     & \bsic{25.66} &       28.33  & \bsic{25.93} &       29.31   & \bsic{22.84} &       24.65   & \bsic{24.35} &       26.69  & \bsic{26.31} &       30.11   & \bsic{24.11} & \Best{26.08} & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \bsic{24.98} &       28.16  & \bsic{25.18} &       29.03   & \bsic{22.62} &       24.89   & \bsic{23.98} &       26.90  & \bsic{25.41} &       29.59   & \bsic{23.64} & \Best{26.05} & \Bsic{todo } &       todo   \\\hline
%			                      & VNLB   $s_t = 2$     & \bsic{27.14} &       28.15  & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{25.43} &       26.06  & \bsic{todo } &       todo    & \bsic{25.18} &       25.81  & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 3$     & \bsic{27.63} &       28.62  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{26.15} &       26.94  & \Bsic{todo } & \Best{todo }  & \Bsic{25.44} & \Best{26.12} & \Bsic{todo } & \Best{todo } \\
%			                      & VNLB   $s_t = 4$     & \Bsic{27.81} & \Best{28.86} & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \Bsic{26.45} & \Best{27.46} & \Bsic{todo } & \Best{todo }  & \Bsic{25.50} & \Best{26.24} & \Bsic{todo } & \Best{todo } \\\hline

@@

In this section we present results obtained with the proposed
method on some classic test sequences with Gaussian noise added.
We consider separatedly the cases of grayscale and color videos.

\subsection{Results on grayscale videos}

We present denoising results on six classic test sequences used commonly in the
literature. We compare against two state-of-the-art methods: V-BM4D
\cite{Maggioni2012}, and the method of Li, Zhang and Dai \cite{LiZhangDai2011}
which we call I-SA-BM4D, since it can be regarded as an iterative version of BM4D \cite{Maggioni2013}
using shape adaptive 3D patches, as in \todo{REF}.  
For V-BM4D, we show results corresponding to two
different choices of parameters. The method labeled V-BM4D-tip
corresponds to the results reported
in \cite{Maggioni2012}. The results labeled V-BM4D-mp were
obtained using the implementation available online \cite{bm4dcode}. This
implementation provides three parameter profiles of increasing quality and
complexity: ``low complexity profile'', ``normal profile'' and ``modified
profile''. We show the results obtained with the modified profile.

Each sequence was contaminated with white Gaussian noise of $\sigma =
10,20,30,40$. Table \ref{tab:psnr-classic-gray} shows the
PSNR values obtained after denoising. For our method, we show results varying the temporal
component of the patch size between $1$ (2D patch) and $4$ frames.
For our method and V-BM4D-mp we show the PSNR of the basic estimate as well.

The best results by a large margin are the ones reported in
\cite{LiZhangDai2011}. This method builds uppon BM4D, which in \cite{Maggioni2013}
is applied to volumetric imagery. In this work, its applicability to video is
also explored, and the results show that it is inferior to V-BM4D, at least 
for moderate noise levels. The method of Li, Zhang and Dai \cite{LiZhangDai2011} 
considers shape adaptive patches, and also several iterations (in each iteration,
the previous iterate is used as an oracle to compute patch distances and the
signal energy in the Wiener filtering step) \todo{Check this}. It seems that both elements
contribute to achieve this significant difference.

We can see that our results are comarable with the ones of V-BM4D. \todo{We need to find new parameters
for grayscale sequences. This discussion needs to be rewritten based on the updated results.}

@@

We compared our method with CIFIC \cite{Dai2013} and V-BM4D \cite{Maggioni2012}, two recent
state-of-the-art methods. As with grayscale videos, for V-BM4D, we show results corresponding to two
different parameter configurations: V-BM4D-tip
corresponds to the results reported
in \cite{Maggioni2012}, and V-BM4D-mp corresponds to the ``modified profile''
of the implementation available online \cite{bm4dcode}.

@@

%		\begin{tabular}{ c | l |c c | c c | c c | c c | c c}
%			\hline
%			\rule{0pt}{10pt}         & Sequence          &\multicolumn{2}{c|}{Bamboo 1}&\multicolumn{2}{c|}{Bandage 1}&\multicolumn{2}{c|}{Cave 4} &\multicolumn{2}{c|}{Market 5}& \multicolumn{2}{c}{Average} \\
%			\rule{0pt}{10pt}$\sigma$ & Method            & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         \\\hline
%			\multirow{1}{*}{$10$}
%			                      & V-BM4D-mp            & \bsic{37.47} &       38.85  & \bsic{38.67} &       40.02  & \bsic{37.30} &       38.40  & \bsic{39.52} &       40.41  & \bsic{38.24} &       39.42  \\
%			                      & VNLB   $s_t = 1$     & \bsic{37.48} &       39.74  & \bsic{39.85} &       41.83  & \Bsic{38.80} & \Best{40.82} & \Bsic{42.16} & \Best{44.10} & \bsic{39.57} &       41.62  \\
%			                      & VNLB   $s_t = 2$     & \bsic{39.01} &       41.10  & \Bsic{40.74} & \Best{42.40} & \bsic{38.70} &       40.65  & \Bsic{42.23} & \Best{44.14} & \Bsic{40.17} & \Best{42.07} \\
%			                      & VNLB   $s_t = 3$     & \bsic{39.40} & \Best{41.37} & \Bsic{40.74} & \Best{42.36} & \bsic{38.50} &       40.35  & \Bsic{42.17} & \Best{44.08} & \Bsic{40.20} & \Best{42.04} \\
%			                      & VNLB   $s_t = 4$     & \Bsic{39.44} & \Best{41.33} & \bsic{40.51} &       42.12  & \bsic{38.30} &       40.05  & \bsic{42.07} &       43.97  & \bsic{40.08} &       41.86  \\\hline
%%
%			\multirow{1}{*}{$20$}
%			                      & V-BM4D-mp            & \bsic{33.23} &       34.70  & \bsic{34.63} &       35.98  & \bsic{33.85} &       34.94  & \bsic{35.30} &       36.13  & \bsic{34.25} &       35.44  \\
%			                      & VNLB   $s_t = 1$     & \bsic{33.19} &       35.53  & \bsic{35.60} &       37.76  & \bsic{35.35} &       37.31  & \bsic{37.90} &       39.88  & \bsic{35.51} &       37.62  \\
%			                      & VNLB   $s_t = 2$     & \bsic{34.95} &       36.93  & \bsic{37.03} &       38.69  & \Bsic{35.60} & \Best{37.52} & \Bsic{38.60} & \Best{40.52} & \bsic{36.55} &       38.41  \\
%			                      & VNLB   $s_t = 3$     & \bsic{35.48} &       37.40  & \Bsic{37.27} & \Best{38.86} & \Bsic{35.54} & \Best{37.43} & \Bsic{38.60} & \Best{40.54} & \Bsic{36.72} & \Best{38.56} \\
%			                      & VNLB   $s_t = 4$     & \Bsic{35.65} & \Best{37.54} & \Bsic{37.26} & \Best{38.84} & \bsic{35.44} &       37.32  & \Bsic{38.50} & \Best{40.48} & \Bsic{36.71} & \Best{38.55} \\\hline
%%
%			\multirow{1}{*}{$40$}
%			                      & V-BM4D-mp            & \bsic{29.07} &       30.46  & \bsic{30.45} &       31.82  & \bsic{30.50} &       31.57  & \bsic{30.93} &       31.74  & \bsic{30.24} &       31.40  \\
%			                      & VNLB   $s_t = 1$     & \bsic{29.25} &       31.57  & \bsic{31.44} &       33.67  & \bsic{31.70} &       33.70  & \bsic{33.47} &       35.44  & \bsic{31.46} &       33.60  \\
%			                      & VNLB   $s_t = 2$     & \bsic{31.18} &       32.99  & \bsic{33.40} &       35.06  & \Bsic{32.60} & \Best{34.61} & \bsic{34.76} &       36.63  & \bsic{32.98} &       34.82  \\
%			                      & VNLB   $s_t = 3$     & \bsic{31.69} &       33.46  & \Bsic{33.76} & \Best{35.32} & \Bsic{32.70} & \Best{34.69} & \Bsic{34.91} & \Best{36.79} & \Bsic{33.27} & \Best{35.07} \\
%			                      & VNLB   $s_t = 4$     & \Bsic{31.88} & \Best{33.64} & \Bsic{33.82} & \Best{35.37} & \Bsic{32.70} & \Best{34.66} & \Bsic{34.89} & \Best{36.77} & \Bsic{33.22} & \Best{35.11} \\\hline
%		\end{tabular}}
		\begin{tabular}{ c | l |c c | c c | c c | c c | c c}
			\rule{0pt}{10pt}         & Sequence          &\multicolumn{2}{c|}{Bamboo 1}&\multicolumn{2}{c|}{Bandage 1}&\multicolumn{2}{c|}{Cave 4} &\multicolumn{2}{c|}{Market 5}& \multicolumn{2}{c}{Average} \\
			\rule{0pt}{10pt}$\sigma$ & Method            & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         \\\hline
			                      & V-BM4D-mp            & \bsic{37.47} &       38.85  & \bsic{38.67} &       40.02  & \bsic{37.30} &       38.40  & \bsic{39.52} &       40.41  & \bsic{38.24} &       39.42  \\
			                      & VNLB   $s_t = 1$     & \bsic{37.00} &       39.57  & \bsic{39.70} &       41.82  & \Bsic{38.58} & \Best{40.77} & \Bsic{42.20} & \Best{44.38} & \bsic{39.37} &       41.64  \\
										 & VNLB   $s_t = 2$     & \bsic{38.46} &       40.85  & \Bsic{40.49} & \Best{42.37} & \Bsic{38.52} & \Best{40.70} & \Bsic{42.22} & \Best{44.38} & \Bsic{39.92} & \Best{42.08} \\
			                      & VNLB   $s_t = 3$     & \bsic{38.87} & \Best{41.19} & \Bsic{40.59} & \Best{42.46} & \bsic{38.42} &       40.60  & \bsic{42.09} &       44.25  & \Bsic{39.99} & \Best{42.13} \\
										 & VNLB   $s_t = 4$     & \Bsic{38.99} & \Best{41.28} & \Bsic{40.55} & \Best{42.42} & \bsic{38.32} &       40.50  & \bsic{41.93} &       44.09  & \Bsic{39.94} & \Best{42.07} \\\hline
			                      & V-BM4D-mp            & \bsic{33.23} &       34.70  & \bsic{34.63} &       35.98  & \bsic{33.85} &       34.94  & \bsic{35.30} &       36.13  & \bsic{34.25} &       35.44  \\
			                      & VNLB   $s_t = 1$     & \bsic{32.99} &       35.58  & \bsic{35.44} &       37.79  & \bsic{34.94} &       37.11  & \bsic{37.80} &       39.83  & \bsic{35.29} &       37.58  \\
			                      & VNLB   $s_t = 2$     & \bsic{34.71} &       36.98  & \bsic{36.90} &       38.78  & \Bsic{35.28} & \Best{37.47} & \Bsic{38.61} & \Best{40.79} & \bsic{36.38} &       38.50  \\
			                      & VNLB   $s_t = 3$     & \bsic{35.18} &       37.40  & \Bsic{37.16} & \Best{38.94} & \Bsic{35.28} & \Best{37.47} & \Bsic{38.67} & \Best{40.83} & \Bsic{36.57} & \Best{38.66} \\
										 & VNLB   $s_t = 4$     & \Bsic{35.34} & \Best{37.54} & \Bsic{37.17} & \Best{38.95} & \Bsic{35.23} & \Best{37.42} & \Bsic{38.59} & \Best{40.72} & \Bsic{36.58} & \Best{38.65} \\\hline
